### 2014-10-31 fundamentals/intro.tex
arrielle's first comment about the long sentence in the intro

The \Cyclus Nuclear Fuel Cycle Simulator framework and 
its modeling ecosystem answer this need for a next generation nuclear fuel cycle 
simulator. Dynamic simulation of nuclear fuel cycles with discrete agents 
and up to isotopic resolution support 
levels of detail appropriate for a varied community of analysts
interested in a range of analysis types. Additionally, \Cyclus employs an 
open development process that supports user access and 
encourages developer extensions.

>>>>

The \Cyclus Nuclear Fuel Cycle Simulator framework and 
its modeling ecosystem answer this need for a next generation nuclear fuel cycle 
simulator. This dynamic simulator employs discrete agents, time, and materials 
up to isotopic resolution in order to support a range of analysis types, levels of 
detail, and fuel cycle analysts.
Additionally, \Cyclus employs a modular architecture and 
open development process that supports user access and 
encourages developer extensions.
